### 2017-07-28 src/4_OnlineLearning.tex

%=======================HASTA ACA REVISADO PROFE =========================
\subsection{Learning algorithms}
In all learning algorithms that are trained from example data, there is a
tradeoff between three factors \cite{dietterich2003}:
\begin{description}
\item[Complexity or capacity of the hypothesis class]

and can be measured by the Vapnik\-Chervonenkis (VC) dimension

@@

Very complex models will fit the training data better (low bias) but it could overfit it and generalise poorly (high variance), this is also called the bias-variance tradeoff.  Generalisation accuracy can sometimes be improved with more training data. The figure \ref{fig:tradeoff} illustrates how generalisation accuracy depends on the complexity of the model and the amount of training data.

>>>>

%=======================HASTA ACA REVISADO PROFE =========================
\subsection{Learning algorithms}
In all learning algorithms that are trained from example data, there is a
tradeoff between three factors \cite{dietterich2003}:
\begin{description}
\item[Complexity or capacity of the hypothesis class] 
 can be measured by the Vapnik\-Chervonenkis (VC) dimension

@@

A very complex models will fit the training data better (low bias) but it could overfit it and generalise poorly (high variance), this is also called the bias-variance tradeoff.  Generalisation accuracy can sometimes be improved with more training data. The figure \ref{fig:tradeoff} illustrates how generalisation accuracy depends on the complexity of the model and the amount of training data.
